Predicting Political Support in the United States

### 2024-03-17 output/paper.qmd
Final changes

@tbl-modelsummarycultural first suggests a that males were less likely to vote for Biden, and more likely to vote for Trump. Looking at @fig-agevsgender-1 this is not an obvious correlation to make with the votes for Biden and Trump being close for each age group, with Trump only winning more votes with the male and above 65 demographic. However, looking at the 90% confidence intervals in @fig-conf_cultural for the coefficients of that model, specifically that for being male, we can see that the model is 90% confident that this relationship is strictly negative, signifying they are against voting for Biden. The model also suggests disagreement within the 45+ community and the agreement within the younger community (18 - 44), something that is evident in @fig-agevsgender-1. @tbl-modelsummarycultural also shows a large correlation between being 30-44 to supporting Biden, with being aged 45-65 or 65+ having very little correlation to support Biden, supported by the 90% confidence interval shown in @fig-conf_cultural for those coefficients spanning both negative and positive, suggesting an uncertain preference. Although the model included being: Female, Asian, 18-29, and Agnostic, in the intercept, for @fig-agevsgender-1, @fig-racevsreligion2, and @fig-racevsreligionlarge-1, @fig-racevsreligionlarge-2 and @fig-racevsreligion2 respectively, it reasonable to say that each graph suggests that being Female, Asian, 18-29, and Agnostic has a correlation with voting for Biden, each demographic having a significant amount more votes for Biden than Trump.

>>>>

@tbl-modelsummarycultural first suggests a that males were less likely to vote for Biden, and more likely to vote for Trump. Looking at @fig-agevsgender-1 this is not an obvious correlation to make with the votes for Biden and Trump being close for each age group, with Trump only winning more votes with the male and above 65 demographic. However, looking at the 90% confidence intervals in @fig-conf_cultural for the coefficients of that model, specifically that for being male, we can see that the model is 90% confident that this relationship is strictly negative, signifying they are against voting for Biden. The model suggests disagreement within the 45+ community and the agreement within the younger community (18 - 44), something that is evident in @fig-agevsgender-1. From @tbl-modelsummarycultural we also see a large correlation between being 30-44 to supporting Biden, with being aged 45-65 or 65+ having very little correlation in supporting Biden, supported by the 90% confidence interval shown in @fig-conf_cultural for those coefficients spanning both negative and positive, suggesting an uncertain preference. Although the model included being: Female, Asian, 18-29, and Agnostic, in the intercept, for @fig-agevsgender-1, @fig-racevsreligion2, and @fig-racevsreligionlarge-1, @fig-racevsreligionlarge-2 and @fig-racevsreligion2 respectively, it reasonable to say that each graph suggests that being Female, Asian, 18-29, and Agnostic has a correlation with voting for Biden, each demographic having a significant amount more votes for Biden than Trump.
